Exploiting Array Syntax in Fortran for Accelerator Programming

### 2011-06-23 papers/GPUScA-2011/programming-model.tex
Added intro to section.

A question that one may pose is ``\emph{Why Fortran and
  not a more modern language like X?}''  The recent rise in interest
in concurrency and parallelism at the language level driven by
multicore CPUs and manycore accelerators has driven a number of new
language developments, both as novel languages and extensions on
existing ones.  For scientific users, new languages and language
extensions to use novel new architectures present a challenge: how do
developers effectively use them while avoiding rewriting code
and potentially growing dependent on a transient technology that will
vanish tomorrow?

>>>>

A question that one may pose is ``\emph{Why Fortran and not a more modern
  language like X?}''  The recent rise in interest in concurrency and
parallelism at the language level driven by multicore CPUs and manycore
accelerators has driven a number of new language developments, both as novel
languages and extensions on existing ones.  For many scientific users familiar
with Fortran, new languages and language extensions to use novel new
architectures present a challenge: how do they effectively use them while
avoiding rewriting code and potentially growing dependent on a transient
technology that will vanish tomorrow?

In this section we present the Fortran subset employed in this paper.  This
subsetting language will allow scientific programmers to stay within the Fortran
language and yet have direct access to GPU hardware.  We first examine how this
programming model relates to work in other languages.
